---
title: "1. Intro"
author: "DrPH Yr 1 Sem 1 2019/2020"
date: "14/12/2019"
output: 
  html_document:
    toc: yes
    toc_float:
      collapsed: no
---

# Instruction

DrPH Yr 1 Sem 1 2019/2020 Mock Exam

- Time 9am - 12pm

0. Preparation (~15 min) 

- 9.30am - 9.45am

1. Check each computer have (latest) R software
- Start Menu -> R
- latest is 3.6.2

```{r, eval=F}
install.packages("installr")
library(installr)
updateR()
```

2. Close R
3. Check each computer have (latest) RStudio IDE Software

- Start Menu -> RStudio
- Help -> About RStudio
- latest: 1.2.5019

4. Open MockExam Project

- New Project
- Version Control
- Git
- Repository URL : https://github.com/puterabemi/MockExam.git
- Project Directory Name : MockExam
- Subdirectory : ~/Rstudio

5. Run Code below (Common Packages)

## 1. - Load Common Packages

```{r, eval=F}
install.packages("pacman")
library(pacman)
p_load(haven, foreign, broom, tidyverse, psych, corrplot, knitr, LogisticDx, generalhoslem, ResourceSelection, lubridate, survival, survminer)
```

## 2. ANOVA (15 - 30min)

- 10am - 10.15am

*constructing*

## 3. ANCOVA (15 - 30min)

- 10.20am - 10.35am

*constructing*

## 4. RM ANOVA (15 - 30min)

- 10.40am - 10.55am

*constructing*

## 5. Linear Regression (15 - 30min)

- 11am - 11.15am

1. Go to Files Tab
2. Open 5 - Linear Regression.Rmd file
3. Follow Instruction in the file

## 6. Logistic Regression (15 - 30min)

- 11.20am - 11.35am

1. Go to Files Tab
2. Open 6 - Logistic Regression.Rmd file
3. Follow Instruction in the file

## 7. Survival Analysis (15 - 30min)

- 11.40am - 11.55am

1. Go to Files Tab
2. Open 7 - Survival Analysis.Rmd file
3. Follow Instruction in the file

## 8. Others (Theories) (30 - 45min)



## 9. Answer


