---
title: "5 - Linear Regression"
author: "DrPH Yr 1 Sem 1 2019/2020"
date: "12/15/2019"
output: html_document
---

```{r}
library(readxl)
data1 <- read_excel('data.xlsx')
head(data1)
```

```{r}
library(tidyverse)
data1 <- data1 %>% mutate(Sex = as.factor(Sex),
                          Age = as.double(Age),
                          BMI = as.double(`Body mass index`),
                          HbA1c = as.double(HbA1c),
                          HDL = as.double(HDL),
                          LDL = as.double(LDL),
                          TG = as.double(TG),
                          Diab_dur = as.double(`Diabetes Age`))
head(data1)
```

# PYQ 2018 linear

Using the dataset analyze the relationship between HbA1c and age,  diabetic duration, bmi

a. Write regression model and regression equation (10m)

b. Add interaction. (age and diabetic duration) Present in table (10m)

c. Write equation with interaction. (10m)

d. Assumptions for fitness analysis for this model. (10m)
**comment on adjusted R-squared

#PYQ 2017 linear

Using the same dataset, analyze the relationship between variable ‘hdl’ and these covariates, ‘ldl’,tg,’gender’. Name the model as Model A. 

a) Write the regression model and regression estimate. (10 marks) 

b) Interpret the variances between regression model and regression estimates (10 marks) 
	
c) Add on interaction between ‘tg and ‘gender’ to the model and name the model as Model B. Compare model A and model B using appropriate test and interpret the findings. (10 marks) 

d) Predict the mean hdl level in a population with ldl = 3.5, tg = 3.0, gender = male  according the Model A and Model B. (10 marks)













