---
title: "6 - Logistic Regression"
author: "DrPH Yr 1 Sem 1 2019/2020"
date: "12/15/2019"
output: html_document
---

A dataset(coronary.csv) contains these variables:

- id : unique identification number
- cad : Coronary Artery Disease (no cad/cad)
- sbp : Systolic Blood Pressure in mmHg
- dbp : Dystolic Blood Pressure in mmHg
- chol : Total Serum Cholesterol in mmol/l
- age : Age in Years
- bmi : BMI in kg/m2
- race : Races (indian/chinese/malay)
- gender : gender (woman/man)


```{r}
# PESANAN PENAJA : RUN THIS CHUNK FIRST BEFORE YOU START THE ANALYSIS!!
library(foreign)
data0 <- read.spss('coronary.sav', to.data.frame = TRUE, convert.factors = T)
data0
```

```{r}
#CODE
glm(outcome ~ var1 + var2 + var3 + var4 + var5, family = binomial(link = logit), data = dataset)
expand.grid(var1 = value2, var2 = value2)
predict(modelname, newdata = nameofnewdata, type = 'link/term/response')
```



**QUESTION 1**

Analyze the relationship between variable ‘cad’ and these covariates, ‘age’,’gender’,’race’ and ‘chol’ and 'dbp'. Name the model as ‘mod.cad’. Write the estimated regression parameters in a table based on ‘mod.cad’. Interpret the parameters. (20 marks)

**QUESTION 2**

Add an interaction term between variable ‘age’ and ‘gender’ to the model ‘mod.cad’.Run the analysis and name the model as ‘mod.cad.int’. Write the estimated regression parameters in a table based on ‘mod.metab.int’.
(10 marks)

**QUESTION 3**

Compare model ‘mod.cad.int’ and ‘mod.cad’ using an appropriate test and interpret the result. (10 marks)

**QUESTION 4**

Predict the logit and probability for having coronory artery disease (cad = cad) in a population with age = 50, gender = woman, race = chinese and dbp = 90, chol = 7 based on ‘mod.cad’ and ‘mod.mcad.int’. (20 marks)



































