---
title: "Answer: 7 - Survival Analysis"
author: "DrPH Yr 1 Sem 1 2019/2020"
date: "14/12/2019"
output: 
  html_document:
    toc: yes
    toc_float:
      collapsed: no
---

# Dataset

Dataset stroke_outcome.dta had these variables

- ID : unique identification number
- sex : patient's gender (male/female)
- race : ethnicity (malay/chinese)
- doa : date of admission
- dod : date of discharge
- gcs : GCS score
- sbp : systolic BP
- dbp : diasolic BP
- age : age of patient during admission (in years)
- event : outcome of patient during date of discharge (censored/dead)
- dm2 : DM status (no/yes)
- hpt2 : Hpt status (no/yes)
- race2 : Malay Ethnicity (no/yes)

As a researcher, you interested to find factors associated with survival of stroke patient.

```{r}
library(pacman)
p_load(haven, foreign, broom, tidyverse, psych, knitr, lubridate, survival, survminer)
mydata <- read_dta("stroke_outcome.dta")
mydata <- mydata %>%
  mutate_if(is.labelled, ~as_factor(.))
mydata <- mydata %>%
  mutate(dur = mydata$doa %--% mydata$dod) %>%
  mutate(dur = as.duration(dur)) %>%
  mutate(dur_days = dur/ddays(1))
mydata
```

# Question 1

Analyse the relationship between variable "event" and these covariate, "sex", "gcs", "sbp" and "age". name the model as "mod.metab".

Write the estimated regression parameter in a table based on "mod.metab"

Interpret the parameter

## Answer

```{r}
mod.metab <- coxph(Surv(time = dur_days, event == "dead")~ sex + gcs + sbp + age,
                   data = mydata)
summary(mod.metab)
tidy(mod.metab)
```

- The log hazard to die change by 0.05 (95% CI = -0.49, 0.59, p = 0.857) for female patient, as compared to male patient, when adjusted to GCS, systolic BP and patient's age.
- The log hazard to die change by -0.23 (95% CI = -0.30, -0.17, p < 0.001) for each increase in 1 unit of GCS, when adjusted to sex, systolic BP and patient's age.
- The log hazard to die change by 0.002 (95% CI = -0.001, 0.009, p = 0.646) for each increase of 1 mmHg of systolic BP, when adjusted to sex, GCS and patient's age.
- The log hazard to die change by 0.018 (95% CI = -0.002, 0.038, p = 0.079) for each increase of 1 year of age, when adjusted to sex, GCS and systolic BP.

# Question 2

add 