---
title: "Answer: 7 - Survival Analysis"
author: "DrPH Yr 1 Sem 1 2019/2020"
date: "14/12/2019"
output: 
  html_document:
    toc: yes
    toc_float:
      collapsed: no
---

# Dataset

Dataset stroke_outcome.dta had these variables

- ID : unique identification number
- sex : patient's gender (male/female)
- race : ethnicity (malay/chinese)
- doa : date of admission
- dod : date of discharge
- gcs : GCS score
- sbp : systolic BP
- dbp : diasolic BP
- age : age of patient during admission (in years)
- event : outcome of patient during date of discharge (censored/dead)
- dm2 : DM status (no/yes)
- hpt2 : Hpt status (no/yes)
- race2 : Malay Ethnicity (no/yes)

As a researcher, you interested to find factors associated with survival of stroke patient.

```{r}
library(pacman)
p_load(haven, foreign, broom, tidyverse, psych, knitr, lubridate, survival, survminer)
mydata <- read_dta("stroke_outcome.dta")
mydata <- mydata %>%
  mutate_if(is.labelled, ~as_factor(.))
mydata <- mydata %>%
  mutate(dur = mydata$doa %--% mydata$dod) %>%
  mutate(dur = as.duration(dur)) %>%
  mutate(dur_days = dur/ddays(1))
mydata
```

# Question 1

Explain the KM Estimation for the survival of the stroke patient

## Answer

The median survival time for the stroke patient was 22 days (95% CI = 12, NA)
```{r}
KM_Overall <- survfit(Surv(time = dur_days, event == "dead")~ 1,
                     data = mydata, type = "kaplan-meier")
KM_Overall
```

KM Plot Shown below
```{r}
ggsurvplot(KM_Overall, data = mydata, risk.table = T)
```

# Question 2

Explain the KM Estimation for the survival of the stroke patient, by DM status (variable:dm2)

## Answer


The median survival time for non DM patient was 29 days (95% CI = 25, NA), while the median survival time for DM patient was 12 days (95% CI = 9, 22). There was significant different of survival time between DM patient and non DM patient (p < 0.001)
```{r}
KM_DM <- survfit(Surv(time = dur_days, event == "dead")~ dm2,
                 data = mydata, type = "kaplan-meier")
KM_DM
```

The KM plot was shown below
```{r}
ggsurvplot(KM_DM, data = mydata, risk.table = T, pval = T)
```


# Question 3

Analyse the relationship between variable "event" and these covariate, "sex", "gcs", "sbp" and "age", by using cox regression. name the model as "mod.metab".

Write the estimated regression parameter in a table based on "mod.metab"

Interpret the parameter

## Answer

```{r}
mod.metab <- coxph(Surv(time = dur_days, event == "dead")~ sex + gcs + sbp + age,
                   data = mydata)
summary(mod.metab)
```

Estimated regression in table
```{r}
tidy(mod.metab)
```

Interpretation

- The log hazard to die change by 0.05 (95% CI = -0.49, 0.59, p = 0.857) for female patient, as compared to male patient, when adjusted to GCS, systolic BP and patient's age.
- The log hazard to die change by -0.23 (95% CI = -0.30, -0.17, p < 0.001) for each increase in 1 unit of GCS, when adjusted to sex, systolic BP and patient's age.
- The log hazard to die change by 0.002 (95% CI = -0.001, 0.009, p = 0.646) for each increase of 1 mmHg of systolic BP, when adjusted to sex, GCS and patient's age.
- The log hazard to die change by 0.018 (95% CI = -0.002, 0.038, p = 0.079) for each increase of 1 year of age, when adjusted to sex, GCS and systolic BP.

# Question 4

Add an interaction term between variable "sex" and "gcs" to the model "mod.metab". Run the analysis and name the model as "mod.metab.int"

Write the estimated regression parameters in a table based on "mod.metab.int"

## Answer

```{r}
mod.metab.int <- coxph(Surv(time = dur_days, event == "dead")~ sex + gcs + sbp + age + sex:gcs,
                       data = mydata)
summary(mod.metab.int)
```

Estimated regression in table

```{r}
tidy(mod.metab.int)
```



# Question 5

Compare model "mod.metab.int" and "mod.metab" using an approprite test and interpret the result

## Answer

the model was compared using chi-square test.

```{r}
anova(mod.metab.int, mod.metab, test = "Chisq")
```

no significant different between model "mod.metab.int" and "mod.metab" (p = 0.223). hence there was no significant interaction between "sex" and "gcs"

# Question 6

Predict probability survival at 14 days when sex = female, gcs = 10, sbp = 110 and age = 75, based on "mod.metab" and "mod.metab.int", as compared to the population average.

## Answer - option 1

Predicted hazard = $h_0(t) \times exp^{(\beta X)}$.

Predicted hazard = base hazard X linear predictor

For **mod.metab model**

base hazard at 14 days was 0.311109196
```{r}
basehaz(mod.metab)
```

linear predictor
```{r}
new_data <- expand.grid(sex = c("female"),
                        gcs = c(10),
                        sbp = c(110),
                        age = c(75))
lp.pred <- predict(mod.metab, newdata = new_data, type = "lp")
0.311109196*exp(lp.pred)
```

The Probability survival at 14 days for the patient, as compared to the population average was `r 0.311109196*exp(lp.pred)`

For **mod.metab model**

base hazard at 14 days was 0.295888040
```{r}
basehaz(mod.metab.int)
```

linear predictor
```{r}
new_data_int <- expand.grid(sex = c("female"),
                            gcs = c(10),
                            sbp = c(110),
                            age = c(75))
lp.pred_int <- predict(mod.metab.int, newdata = new_data_int, type = "lp")
0.295888040*exp(lp.pred_int)
```

The Probability survival at 14 days for the patient, as compared to the population average was `r 0.295888040*exp(lp.pred_int)`

  
## Answer - option 2

For **mod.tab.int**

```{r}
new_data2_int <- expand.grid(sex = c("female"),
                             gcs = c(10),
                             sbp = c(110),
                             age = c(75),
                             dur_days = c(14),
                             event = c("dead"))
pred.exp_int <- predict(mod.metab.int, newdata = new_data2_int, type = "expected")
cbind(new_data2_int, pred.exp_int)
```

the probability survival at 14 days for the patient, as compated to the population average was 0.630

